---
title: "Love vs extraterrestials"
author: "Yasheika Pink"
date: "Spring 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(tigerstats)
help("m111surveyfa13")
mydata<-m111surveyfa13 <- na.omit(m111surveyfa13)
```

# A question of Belief

Your data is in the dataframe called "mydata" examine it in the environment tab  
do a variable analysis on the 3 Questions and then upload the appropriate Rmd template for this job.   
Also create an empty github repository called "Belief" and make it the remote repository for  
this assignment.  For each question supply graphical evidence, numerical summaries, an inferential test, and a conclusion.  When finished push your rmd file, your project file, and your knitted html file to your github repo.  Finally turn in to Canvas the link to your github repo.




# Your First Question  

### Do people who believe in Love at First sight also tend to believe in Life on other planets?

$H_O$: No relation between belief in love at first sight, and belief in ET
$H_A$: There is a relation between belief in love at first sightm and the belief in ET

Graphic display
  
```{r}
barchartGC(~love_first + extra_life,data=mydata)
```

 People who believe in love at first sight, also tend believe in ET.
 Nummerical Summary
 
```{r}
table1 <- xtabs(~love_first + extra_life, data=mydata)
rowPerc(table1)
colPerc(table1)
```
 Looks like the people who believe in love at first sight is about the same as the people of believe in ET. 
 
 Inference
```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```


We fail to reject the null hypothesis, because the p = 0.69 is greater than the P=0.05 
# Your second Question  

### Is there a difference between boys and girls with respect to belief in life on other planets?

$H_O$: No relation between Gender if belief in ET
 $H_A$: There is a relation betwenn gender in the belief in ET

 graphical Summery
```{r}
barchartGC(~sex + extra_life,data=mydata)
```
 It appears that males have more belief in ET
 
 Numerical Summary
```{r}
table1 <- xtabs(~sex + extra_life, data=mydata)
rowPerc(table1)
colPerc(table1)
```
 Summary appears that males belief in ET is greater than females.
 
 Inference
```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```
 
 
 I fail to reject the null hypothesis because the p-value is higher than 0.05
 
 
# Your last Question   

### Is there a difference between boys and girls with respect to belief in love at First sight?
Graphical Summary
```{r}
barchartGC(~sex + love_first,data=mydata)
```
It appears that males do not believe in love a first sight

numerical summary
```{r}
table1 <- xtabs(~sex + love_first, data=mydata)
rowPerc(table1)
colPerc(table1)
```

Summary appears that males do not believe in love at first sight.

Inference
```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```
SH_O$: No relation between belief in love at first sight, and belief in ET
$H_A$: There is a relation between belief in love at first sightm and the belief in ET  

I fail to reject the null hypothesis. Boys do not believe in love at first sight.